% Document class and font size
\documentclass[a4paper,10pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, margin=0.8in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks
\usepackage{kotex}
\usepackage{graphicx}
\usepackage{array}
\usepackage{longtable}
\usepackage{tasks}
\usepackage{setspace}
\usepackage{soul}

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing
\graphicspath{{../../pictures}}
\setlength\parindent{8pt} %no indentation

% Begin document
\begin{document}
% Disable page numbers
\pagestyle{empty}
% Enable page numbers
% \pagenumbering{arabic}

% Vertical center alignment
\pagebreak
\hspace{0pt}
\vfill
% Vertical center alignment

% Header
\begin{spacing}{1.2}
	\normalsize January 27, 2025 \hfill\large\textbf{HYPEBEAST Korea Recruitment Team}\\
	\normalsize \null\hfill HYPEBEAST Korea Co., Ltd.\\
	\normalsize \null\hfill 818, Seolleung-ro, Gangnam-gu,\\
	\null\hfill Seoul, South Korea, 06014\\
\end{spacing}

Dear respected person in charge,\\

I'm a motivated salesperson from the renowned fashion concept store 8DIVISION. I have intense experiences with international communications with high-fashion clients and creative social media marketing. At the same time, I'm also an expert AI researcher and data scientist with a Master's degree and career.

Over the last year, I shifted my career from scientific research to fashion through 8DIVISION, to fulfill my enlonged love towards the industry. By utilizing my tech-savvy knowledge, fluent language skills, and passion for the team, I could reach an extensive amount of opportunities and people with delight.

Your opening responsibilities assert the following: Strong communication skills with advertisement clients worldwide; creative and customizable ideas for clients to prioritize Hypebeast’s resources; and systematical task arrangement and pipelining for frictionless workflows.

Over 4+ years of expert AI research, I've been communicating with field clients, both domestic and international, with complex and abstract AI concepts. Organizing the ideas and clarifying through visualization and speech have been my first-of-all priority. These skills can be verified through my 2 science journal publications, 6 conference presentations, and numerous project and meeting experiences.

For the last year in 8DIVISION, I have applied those skills to the fashion industry including interpretation for buyer meetings, store introduction and sales for international clients, long-term sales data visualization, robotic work processes automation, high-level communication with technicians, and more.

I also creative-directed the store's Instagram account \href{https://instagram.com/8division_journal}{@8division$\_$journal} \textit{from scratch}, that is, from concept suggestion to styling, modeling, photo and videography, editing, and posting. We could raise followers from 5,700 to 7,000, reach 455\%, and engage 425\% compared to the past (before May 2024). These successes could be derived from customized strategies: posting more active and dynamic content like reels, daily stories, store-visitor content, and brand tags for higher reach.

Additionally, I have reorganized the work settings to be more efficient in the 8DIVISION team by introducing collaboration tools (Notion, Microsoft365, Google Docs), modifying existing Excel forms to be more usable, and updating work routines in coordination with our logistics and online teams.

Based on my expertise background knowledge of engineering and passion for the fashion industry, I can firmly tell that \textit{I've been a proactive and analytical explorer for improved solutions throughout my whole career.} Now I'm willing and looking forward to leveraging my strengths and continuing my journey at Hypebeast Korea as a Brand Partnership Manager.

I have attached my curriculum vitae and personal portfolio to the application form. Also, the portfolio website links are listed below. Hope this finds you well, and I'll be looking forward to hearing from you.\\


Sincerely yours,\\

\begin{spacing}{1.2}
	\noindent
	\textbf{\large Hyeonbeen Lee}\\
	\normalsize
	6-3, Hoenamu-ro 39gil, Yongsan-gu,\\
	Seoul, South Korea, 04344
\end{spacing}
\small
\noindent
\begin{tabular}{@{}ll}
	\textbf{Mobile: }         & \href{tel:+82-10-6236-4693}{+82-10-6236-4693}                                                                 \\
	\textbf{EMail: }          & \href{mailto:edward.hyeonbeen.lee@gmail.com}{edward.hyeonbeen.lee@gmail.com}                                  \\
	\textbf{Instagram: }      & \href{https://www.instagram.com/leehyeonbeen}{@leehyeonbeen}                                                  \\
	\textbf{GitHub: }         & \href{https://github.com/leehyeonbeen}{github.com/leehyeonbeen}                                               \\
	\textbf{LinkedIn: }       & \href{https://www.linkedin.com/in/hyeonbeen-lee-239500286/}{linkedin.com/in/hyeonbeen-lee-239500286}          \\
	\textbf{Google Scholar: } & \href{https://scholar.google.com/citations?user=TiduRxoAAAAJ}{scholar.google.com/citations?user=TiduRxoAAAAJ} \\
\end{tabular}
\newline\newline
\noindent\large\textit{Attached: Curriculum vitae, personal portfolio}

% Vertical center alignment
\vfill
\hspace{0pt}
\pagebreak
% Vertical center alignment
\end{document}